\section*{Appendix}
\subsection*{Appendix A: 10-Q and 8-K parsing}
\label{appa}
We develop a Python program to automatically parse, process and retrieve 10-K and 8-K filings from EDGAR database. Our algorithm consists of the following steps:

1. Download all quarterly master indexes from EDGAR using \textit{python-edgar}\footnote{Python-edgar package documentation available at \url{https://github.com/edouardswiac/python-edgar/blob/master/README.md}} package.

2. Filter all 10-Q and 8-K filings\footnote{Our analyses exclude amendments such as 10-Q/A and 8-K/A} from EDGAR master index files and obtain url of the \textit{filing detail} webpage\footnote{One example of filing detail webpage is available at \url{https://www.sec.gov/Archives/edgar/data/320193/000032019320000050/0000320193-20-000050-index.html}} for each of the 10-Q and 8-K filings. 

3. Extract (a) identification information\footnote{For example cik, accession number, reporting period, filing date and 8-K items etc.} and (b) url of report in HTM/TXT format\footnote{One example of report in HTM format is available at \url{https://www.sec.gov/Archives/edgar/data/320193/000032019320000050/a8-kq220203282020.htm}. We first search for url of main report in HTM format. If HTM format main report is not available, then we extract the url of TXT format full report. Each EDGAR filing can be accessed in three formats at maximum: regular text (*.txt), web pages (*.htm) and eXtensible Business Reporting Language, also known as XBRL (*.xml). Early filings in EDGAR are only in TXT format. Later filings extend to HTM format, and in 2009 SEC adopted the XBRL for all corporate filings \cite{secFinalRuleInteractive2009}. Therefore, current existing EDGAR filings all contain a TXT file, and depending on their filing date and company reporting policy they may or may not contain HTM or XML files. Normally all filings in XML format are also available in HTM format. We manually checked 100 random filings that are in XML format, and all of them are also available in HTM format with the same content. The TXT files usually contain not only the main report, but also all other additional filing materials (if any) such as graphics, exhibits and press release etc. However, the HTM files only contain the main report. We mainly focus on HTM files other than TXT files because the former naturally filters out less relevant information, and provides a cleaner textual content of the essential information. XML files are not parsed due to low tractability. } from the \textit{filing detail} webpage for each of the 10-Q and 8-K filings. 

4. Parse and cleanse\footnote{Cleansing steps are: (a) delete nondisplay section; (b) delete all tables that contains more than 4 numbers; and (c) delete all HTML tags} all 10-Q and 8-K filings with url of HTM/TXT format report, using \textit{beautiful soup}\footnote{Beautiful soup package documentation available at \url{https://www.crummy.com/software/BeautifulSoup/bs4/doc/}} package. 

5. Save all clean 10-Q and 8-K filings to local device. 

6. Perform word count on clean 10-Q and 8-K filings using LM dictionary.\footnote{LM dictionary available at \url{https://sraf.nd.edu/textual-analysis/resources/\#LM\%20Sentiment\%20Word\%20Lists}}

7. Calculate the Gunning fog index using \textit{textstat}\footnote{textstat package documentation available at \url{https://github.com/shivam5992/textstat}} package. 

All Python scripts and data are available online via \url{https://github.com/fengzhi22/narrative_conservatism}.

\subsection*{Appendix B: Textual Variable Definition}
\label{appb}
\begin{table}[H]
	\centering
	\begin{tabular}{lp{15cm}p{15cm}}
		\textbf{Variable} & \textbf{Definition} \\
		NW & Number of words, defined as the natural logarithm of one plus the count of total words (nw)\\
		nw & Raw count of total words\\
		TONE & Tone, defined as the number of net positive words per thousand total words, calculated as the total number of positive words minus the sum of total number of negative words and the total number of negations, and multiply the previous result by one thousand\\
		TLAG & Time lag, defined as the number of natural days elapsed between the news release date and the document filing date. In 10-Q sample, it is the number of natural days elapsed between the fiscal quarter-end date and the 10-Q filing date in EDGAR. In 8-K sample, it is the number of natural days elapsed between the 8-K filing date and its nearest news day, defined as a date whose change in daily return ($\Delta$DRET) is three times larger than the firm’s average change in daily return over the calendar year\\
		READ & Gunning fog index, calculated as the average words per sentence plus the percent of complex words and multiply the sum by 0.4 \\
		ABTONE & Abnormal tone, calculated as the residual of the cross-sectional expected tone model (Equation 3)\\
		N8K & Number of 8-K filings in one reporting period date \\
		NITEM & Number of 8-K items in one reporting period date \\
		
	\end{tabular}%
\end{table}%

\subsection*{Appendix C: Financial Variable Definition}
\label{appc}
\begin{table}[H]
	\centering
	\begin{tabular}{lp{15cm}p{15cm}}
		\textbf{Variable} & \textbf{Definition} \\
		
		EARN & Quarterly earnings, defined as quarterly earnings before extraordinary items (Compustat data item IBQ) scaled by beginning-of-quarter total assets (Compustat data item ATQ) \\
		$\Delta$EARN & Change in quarterly earnings, defined as current quarterly earnings minus one-quarter-lagged quarterly earnings \\
		LEV & Leverage ratio, defined as beginning-of-quarter short term debt (Compustat data item DLCQ) plus beginning-of-quarter long term debt (Compustat data item DLTTQ) scaled by beginning-of-quarter total assets (Compustat data item ATQ) \\
		MTB & Market-to-book ratio, defined as beginning-of-quarter market value of equity, calculated as common share price (Compustat data item PRCCQ) times common shares outstanding (Compustat data item CSHOQ) divided by beginning-of-quarter book value of equity (Compustat data item CEQQ) \\
		SIZE & Firm size, defined as the natural logarithm of market value of equity, calculated as natural logarithm of common share price (Compustat data item PRCCQ) times common shares outstanding (Compustat data item CSHOQ) \\
		QRET & Quarterly market-adjusted stock return, defined as buy-and-hold stock return (CRSP data item RET) over the fiscal quarter adjusted by the value-weighted stock return (CRSP data item VWRETD) over the same period \\
		DRET & Daily market-adjusted stock return, defined as daily buy-and-hold stock return (CRSP data item RET) adjusted by the daily value-weighted stock return (CRSP data item VWRETD)\\
		$\Delta$DRET & Change in daily market-adjusted stock return (DRET), defined as current daily market-adjusted stock return minus one-day-lagged daily market-adjusted stock return \\
		NEG & Indicator for negative quarterly return, which is set to 1 when market-adjusted stock return (QRET) is negative and 0 otherwise \\
		BN & Indicator for daily bad news, which is set to 1 (0) if the negative (positive) change in daily market-adjusted stock return ($\Delta$DRET) is three times larger than the firm’s average decrease (increase) in daily return over the calendar year.\\
		AF & Analyst forecast, defined as analysts' mean consensus forecast for one-year-ahead earnings per share, scaled by stock price per share at the end of the fiscal quarter (Compustat data item PRCCQ)\\
		AFE & Analyst forecast error, defined as I/B/E/S earnings per share minus the median of the most recent analysts' forecasts, deflated by stock price per share at the end of the fiscal quarter (Compustat data item PRCCQ)\\
		BUSSEG & Business segment, defined as the natural logarithm of one plus number of business segments, or one if item is missing from Compustat\\
		GEOSEG & Geographical segment, defined as the natural logarithm of one plus number of geographical segments, or one if item is missing from Compustat\\
		AGE & Firm age, defined as the natural logarithm of one plus number of days elapsed since the firm's first entry date in CRSP\\
		STD\_EARN & Standard deviation of quarterly earnings (EARN) over the last five quarters\\
		STD\_QRET & Standard deviation of monthly market-adjusted stock return over all months in the fiscal quarter\\
		LOSS & Indicator for loss, which is set to 1 when quaterly earnings (EARN) is negative and 0 otherwise\\
	\end{tabular}%
\end{table}%

\newpage
\subsection*{Appendix D: 8-K Item List}
\label{appd}
\input{../output/table/appd}

\newpage
\begin{small}
\subsection*{Appendix E: 8-K Matching Cases}
We check whether the 8-K filings are responses to their matched news releases, as proxied by dramatic market movements. First, we randomly pick 20 good and bad news events. Next, we read the 8-Ks matched to the news and check if the corporate events depicted in the 8-Ks are in line with the market movements both in terms of direction and magnitude. We find that the 8-K matching cases make economic sense overall. See selected 8-K matching cases below.
\label{appe}
\begin{center}
	\textbf{Good News}
\end{center}
\subsubsection*{Case 1: Drug Test Results Announcement; TLAG = 2}
Opexa Therapeutics, Inc. (CIK = 0001069308) experienced a significant rise in market-adjusted daily stock returns ($\Delta$DRET = 2.67) on September 8 of 2009. On September 10 of 2009, the company filed an 8-K with ending reporting period on September 8 of 2009, which contained Item 8.01: Other Events and Item 9.01: Financial Statements and Exhibits. This 8-K stated that ``On September 8, 2009, Opexa Therapeutics, Inc. (the `Company') issued a press release reporting additional analyses of TERMS data for Tovaxin®, a personalized T-cell immunotherapy for multiple sclerosis (MS)". 
\subsubsection*{Case 2: Sales of Equity Securities; TLAG = 6}
MiddleBrook Pharmaceuticals, Inc. (CIK = 0001161924) experienced a significant rise in market-adjusted daily stock returns ($\Delta$DRET = 1.43) on January 24 of 2008. On January 30 of 2008, the company filed an 8-K with ending reporting period on January 24 of 2008, which contained Item 1.01: Entry into a Material Definitive Agreement, Item 3.02: Unregistered Sales of Equity Securities and Item 9.01: Financial Statements and Exhibits. This 8-K stated that ``On January 24, 2008, Middlebrook Pharmaceuticals, Inc. (the `Company') entered into a Securities Purchase Agreement (the `Securities Purchase Agreement') with selected accredited investors (the `Investors'), to sell an aggregate of approximately 8,750,000 shares (the `Shares') of the Company’s common stock, par value \$0.01 per share (the `Common Stock'), and warrants to purchase an aggregate of approximately 3,500,000 shares of Common Stock (the `Warrant Shares') at an exercise price of \$3.00, subject to certain adjustments (the `Warrants' and, together with the Shares, the `Units'), at a price of \$2.40 per Unit, resulting in gross proceeds to the Company of \$21 million (the 'Offering')".
\subsubsection*{Case 3: Entry into an Agreement; TLAG = 6}
SinoCoking Coal and Coke Chemical Industries, Inc. (CIK = 0001099290) experienced a significant rise in market-adjusted daily stock returns ($\Delta$DRET = 1.38) on September 9 of 2014. On September 15 of 2014, the company filed an 8-K with ending reporting period on September 9 of 2014, which contained Item 8.01: Other Events and Item 9.01: Financial Statements and Exhibits. This 8-K included a press release, which stated that ``SinoCoking Coal and Coke Chemical Industries, Inc. (Nasdaq:SCOK), a vertically-integrated coal and coke processor, today said it has signed an exclusive agreement with both the Institute of Process Engineering of the Chinese Academy of Sciences and the North China Institute of Science and Technology to refine and implement a technology that will be used, beginning next month, to convert the 21 million tons of coal at four SinoCoking underground mines into syngas, a clean burning fuel".
\subsubsection*{Case 4: Entry into a Material Definitive Agreement; TLAG = 8}
E-Net, Inc. (CIK = 0001012481) experienced a significant rise in market-adjusted daily stock returns ($\Delta$DRET = 1.19) on September 15 of 1999. On September 23 of 1999, the company filed an 8-Ks with ending reporting period on September 15 of 1999. The 8-K contained Item 5: Other events and Item 7: Financial statements and exhibits. The 8-K stated that ``E-Net, Inc. (Nasdaq: ETEL) and IXC Communications, Inc. (Nasdaq: IIXC) have signed a definitive agreement to jointly develop and market the Internet Telephony services of e-Net's wholly owned subsidiary, ZeroPlus.com, Inc., to consumers and businesses around the world".
\subsubsection*{Case 5: Sales of Equity Securities; TLAG = 6}
ReWalk Robotics Ltd. (CIK = 0001607962) experienced a significant rise in market-adjusted daily stock returns ($\Delta$DRET = 1.19) on June 5 of 2019. On June 11 of 2019, the company filed an 8-K with ending reporting period on June 5 of 2019, which contained Item 1.01: Entry into a Material Definitive Agreement, Item 3.02: Unregistered Sales of Equity Securities, Item 8.01: Other Events and Item 9.01: Financial Statements and Exhibits. This 8-K stated that ``On June 5, 2019  and June 6, 2019, ReWalk Robotics Ltd. (the `Company') entered into warrant exercise agreements (the `Exercise Agreements') with certain institutional investors (the `Holders') of warrants to purchase the Company’s ordinary shares (the `Public Warrants'), par value NIS 0.25 per share (the `Ordinary Shares'), previously issued in the Company’s follow-on offering in November 2018, pursuant to which the Holders agreed to exercise in cash their Public Warrants to purchase an aggregate of 1,464,665 Ordinary Shares at the existing exercise price of \$7.50 per share, for gross proceeds (before placement agent fees and expenses of approximately \$1 million) to the Company of approximately \$11 million".

\newpage
\begin{center}
	\textbf{Bad News}
\end{center}
\subsubsection*{Case 1: Disposition of Assets; TLAG = 1}
Media Services Group, Inc. (CIK = 0000014280) experienced a significant drop in market-adjusted daily stock returns ($\Delta$DRET = -3.26) on April 13 of 2004. On April 14 of 2004, the company filed an 8-K with ending reporting period on the same day, which contained Item 2: Acquisition or disposition of assets. This 8-K stated that ``On March 31, 2004, Media Services Group, Inc. (the `Company') completed its sale of substantially all of the assets relating to its telemarketing sales and teleservices business held by its wholly-owned subsidiary, MKTG Teleservices, Inc. to SD\&A Teleservices, Inc. (`SD\&A'), a Georgia corporation and wholly-owned
subsidiary of the Robert W. Woodruff Arts Center, Inc. for \$3.3 million in cash plus the assumption of certain liabilities relating to such business, subject to
a final working capital adjustment, pursuant to a definitive agreement entered into as of March 31, 2004".
\subsubsection*{Case 2: Termination of a Material Definitive Agreement; TLAG = 0}
Ocean Power Technologies, Inc. (CIK = 0001378140) experienced a significant drop in market-adjusted daily stock returns ($\Delta$DRET = -3.26) on June 2 of 2016. On June 2 of 2016, the company filed two 8-Ks with ending reporting period on the same day, which contained Item 1.02: Termination of a Material Definitive Agreement, Item 1.01: Entry into a Material Definitive Agreement and Item 9.01: Financial Statements and Exhibits. The first 8-K stated that ``On June 2, 2016, Ocean Power Technologies, Inc. (the `Company') and Rodman \& Renshaw, a unit of H. C. Wainwright \& Co., LLC (the `Manager'), agreed to terminate the At the Market Offering Agreement (the `Offering Agreement') dated October 19, 2015, as amended, between the Company and the Manager, relating to the offering and sale of shares of the Company’s common stock, par value \$0.001 per share, having an aggregate offering price of up to \$2,906,836 from time to time through or to the Manager, in an `at the market offering.' The termination of the Offering Agreement is effective immediately and the at the market offering program is no longer available for use by the Company".
\subsubsection*{Case 3: Departure of Directors or Certain Officers; TLAG = 0}
Catuity Inc. (CIK = 0001109740) experienced a significant drop in market-adjusted daily stock returns ($\Delta$DRET = -3.16) on June 22 of 2005. On June 22 of 2005, the company filed an 8-K with ending reporting period on the same day, which contained Item 5.02: Departure of Directors or Certain Officers; Election of Directors; Appointment of Certain Officers: Compensatory Arrangements of Certain Officers. This 8-K stated that ``On Friday June 17, 2005 Catuity learned of the unfortunate and unexpected death of Mr. Alan L. Gilman, one of the Company's members of its Board of Directors. Mr. Gilman died of a heart attack despite having no history of heart trouble". 
\subsubsection*{Case 4: Vote of Security Holders; TLAG = 4}
Biostar Pharmaceuticals, Inc. (CIK = 0001418133) experienced a significant drop in market-adjusted daily stock returns ($\Delta$DRET = -2.19) on June 9 of 2016. On June 13 of 2016, the company filed an 8-K with ending reporting period on June 9 of 2016, which contained Item 5.07: Submission of Matters to a Vote of Security Holders. This 8-K stated that ``On June 9, 2016, Biostar Pharmaceuticals, Inc. (the `Company') held its Annual Meeting of Shareholders at its executive offices in Xianyang City, Shaanxi Province, People's Republic of China. Set forth below are the matters voted upon at the meeting and the voting results. On the record date of April 13, 2016, there were 2,212,188 shares of the Company's common stock issued and outstanding. Proposal 1 (Election of Directors) - The shareholders elected Ronghua Wang, King-fai Leung, Haipeng Wu, Zhongyang Shang and Qinghua Liu as directors of the Company to hold office until the next annual meeting of shareholders and until their successors are duly elected. Proposal 2 (Ratification of Auditors) - The Company's shareholders voted to ratify the appointment of Mazars CPA Limited as the Company's independent registered public accounting firm for the year ending December 31, 2015 with 1,510,989 shares voting for and 25,326 shares voting against (15,431 shares abstaining)".
\subsubsection*{Case 5: Receiving a Request for Clarification from the Stock Exchange; TLAG = 3}
My Size, Inc. (CIK = 0001211805) experienced a significant drop in market-adjusted daily stock returns ($\Delta$DRET = -1.86) on February 14 of 2017. On February 17 of 2017, the company filed an 8-K with ending reporting period on February 14 of 2017, which contained Item 8.01: Other Events and Item 9.01: Financial Statements and Exhibits. This 8-K stated that ``On February 14, 2017, the Company received a verbal request from the Tel Aviv Stock Exchange to clarify to the public the difficulties which hindered the possibility of transferring the Company's shares from market to market. In response to such request, the Company filed a report which contained the following statement..."
\end{small}