%%%%%%%%%%%%%% Table 1: Sample Selection Process
\input{../output/table/T1}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%% TABLE 2 Panel A + TABLE 2 Panel B
%\begin{landscape}
\input{../output/table/T2PA}
\input{../output/table/T2PB}
Table 2 Panel A and Table 2 Panel B present summary statistics for key variables in 10-Q and 8-K sample. All financial variables except returns are winsorized at 1\% and 99\% level. See \hyperref[appb]{Appendix B} and \hyperref[appc]{Appendix C} for textual and financial variable definitions.
%\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%% TABLE 2 Panel C + TABLE 2 Panel D
\newpage
\begin{landscape}
\input{../output/table/T2PC}
\input{../output/table/T2PD}
Table 2 Panel C and Table 2 Panel D present correlation matrix for key variables in 10-Q and 8-K sample. Pearson (Spearman) correlations are exhibited above (below) diagonal. See \hyperref[appb]{Appendix B} and \hyperref[appc]{Appendix C} for textual and financial variable definitions. All financial variables except returns are winsorized at 1\% and 99\% level. 
\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%% TABLE 3 Panel A
\newpage
%\begin{landscape}
\input{../output/table/T3PA}
\setcounter{equation}{0}
\begin{equation}
TEX_{i,t}=\beta_0+\beta_1QRET_{i,t}+\beta_2NEG_{i,t}+\beta_3QRET_{i,t}\times NEG_{i,t}+\beta_nCONTROLS_{i,t}+\epsilon_{i,t}
\end{equation}

Table 3 Panel A presents regression results of Equation (1). TEX represents a vector of textual properties that consists of number of words (NW), tone (TONE) and reporting time lag (TLAG). CONTROLS denotes a vector of control variables including firm size (SIZE), market-to-book ratio (MTB) and leverage ratio (LEV). See \hyperref[appb]{Appendix B} and \hyperref[appc]{Appendix C} for textual and financial variable definitions. All financial variables except returns are winsorized at 1\% and 99\% level. Column 2, 4 and 6 include firm and time fixed effects and standard errors are clustered at industry level identified by 4-digit SIC codes. ***, ** and * indicate significance at the 1\%, 5\% and 10\% levels in a two-tailed test.
%\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%% TABLE 3 Panel B
\newpage
\input{../output/table/T3PB}
\setcounter{equation}{3}
\begin{equation}
ABTONE_{i,t}=\beta_0+\beta_1QRET_{i,t}+\beta_2NEG_{i,t}+\beta_3QRET_{i,t}\times NEG_{i,t}+\beta_nCONTROLS_{i,t}+\epsilon_{i,t}
\end{equation}
\begin{equation}
\begin{split}
TONE_{i,t}=\beta_0+\beta_1QRET_{i,t}+\beta_2NEG_{i,t}+\beta_3QRET_{i,t}\times NEG_{i,t}+\beta_nCONTROLS_{i,t}+\epsilon_{i,t}
\end{split}
\end{equation}

Table 3 Panel B presents regression results of Equation (4) (Column 1 and 2) and Equation (5) (Column 3 and 4). CONTROLS denotes a vector of control variables including firm size (SIZE), market-to-book ratio (MTB), leverage ratio (LEV) and all other regressors in \hyperref[eq2]{Equation 2}. See \hyperref[appb]{Appendix B} and \hyperref[appc]{Appendix C} for textual and financial variable definitions. All financial variables except returns are winsorized at 1\% and 99\% level. Column 2 and 4 include firm and time fixed effects and standard errors are clustered at industry level identified by 4-digit SIC codes. ***, ** and * indicate significance at the 1\%, 5\% and 10\% levels in a two-tailed test.

%%%%%%%%%%%%%%%%%%%%%%%%% TABLE 4 Panel A
\newpage
%\begin{landscape}
\input{../output/table/T4PA}
\setcounter{equation}{2}
\begin{equation}
TEX_{i,t}=\beta_0+\beta_1\Delta DRET_{i,t-tlag}+\beta_2BN_{i,t-tlag}+\beta_3\Delta DRET_{i,t-tlag}\times BN_{i,t-tlag}+\beta_nCONTROLS_{i,t}+\epsilon_{i,t}
\end{equation}

Table 4 Panel A presents regression results of Equation (3). Column 1-6 and Column 7 show results of the full 8-K sample and of the subsample for TLAG$>$0, respectively. TEX represents a vector of textual properties that consists of number of words (NW), tone (TONE) and reporting time lag (TLAG). CONTROLS denotes a vector of control variables including firm size (SIZE), market-to-book ratio (MTB) and leverage ratio (LEV). See \hyperref[appb]{Appendix B} and \hyperref[appc]{Appendix C} for textual and financial variable definitions. All financial variables except returns are winsorized at 1\% and 99\% level. Column 2, 4, 6 and 7 include firm and time fixed effects and standard errors are clustered at industry level identified by 4-digit SIC codes. ***, ** and * indicate significance at the 1\%, 5\% and 10\% levels in a two-tailed test.
%\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%% TABLE 4 Panel B
\newpage
%\begin{landscape}
\input{../output/table/T4PB}
\setcounter{equation}{2}
\begin{equation}
TEX_{i,t}=\beta_0+\beta_1\Delta DRET_{i,t-tlag}+\beta_2BN_{i,t-tlag}+\beta_3\Delta DRET_{i,t-tlag}\times BN_{i,t-tlag}+\beta_nCONTROLS_{i,t}+\epsilon_{i,t}
\end{equation}

Table 4 Panel B presents regression results of Equation (3), with TEX being NITEM (Column 1), N8K (Column 2) and TLAG (Column 3) respectively. CONTROLS denotes a vector of control variables including firm size (SIZE), market-to-book ratio (MTB) and leverage ratio (LEV). Column 1 presents the result of an ordinary least square (OLS) regression with firm and time fixed effects and clustered standard errors at industry level identified by 4-digit SIC codes. Column 2 and 3 present the results of ordered logistics models. See \hyperref[appb]{Appendix B} and \hyperref[appc]{Appendix C} for textual and financial variable definitions. All financial variables except returns are winsorized at 1\% and 99\% level. ***, ** and * indicate significance at the 1\%, 5\% and 10\% levels in a two-tailed test.